The Analogue Method for Precipitation Prediction: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2016-12-06 Moving temporal window - HESS/template.tex
Addition of the references.
Addition of a paragraph in the discussion.

%TODO: check references: complete, doi, etc

@@

@@

	Finally, since long meteorological archives are more and more available, the improvements proposed by the MTW especially for days or sequences of heavy precipitation may be interesting even without long continuous precipitation archives. For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available. However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantatively in flood reports. Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.

@@

	\bibliographystyle{copernicus}
	\bibliography{../_refs/4_articles-2016_HESS_moving-window}

>>>>

%TODO: journal abbreviations
%TODO: read again

@@

	The introduction of the MTW improved the selection of synoptic analogues. Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential for application on long meteorological archives. For example, when processing forecasts for a target day with synoptic similarity with situations from the past related to extreme weather, even though no precipitation archive is available. Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. It is thus worth to known that the situation at hand has such analogue in the past. Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available. Indeed, if the selection of analogues with the MTW on the long period differ from the selection on the short period, this may point out a sub-optimal forecast. Finally, other predictands might not need sub-daily total values, but point observations (e.g. hail, or extreme wind gusts).

@@

	Finally, since long meteorological archives are more and more available, the improvements proposed by the MTW especially for days or sequences of heavy precipitation may be interesting even without long continuous precipitation archives. For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available. However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.

@@

	\bibliographystyle{copernicus}
	\bibliography{references}
